Using SMT engine to generate Symbolic Automata\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2017-03-01 2017-Xudong-SMT/OpenPNets-SMT.tex
Commit test
Have chosen a color.

%\usepackage{amsfonts}
%\usepackage{fancyhdr}
%\usepackage{cite}
%\usepackage{ifthen}
%\usepackage{amssymb}
%\usepackage{fancyhdr}
%\usepackage{pifont}
\usepackage{stmaryrd}
\usepackage{mathtools,mathpartir}
\usepackage{proof}
%\usepackage{setspace}
%\usepackage{indentfirst}
\usepackage{amsmath,amssymb,amscd,mathrsfs}
\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}
\usepackage{epsfig,color,subfigure,enumitem}
\newcommand{\TODO}[1]{\textcolor{red}{\textbf{[TODO:#1]}}}
\newcommand{\NOTE}[1]{\textcolor{blue}{\textbf{[NOTE:#1]}}}
\newcommand{\ERIC}[1]{\textcolor{blue}{#1}}
\newcommand{\coloncolon}{{:\hspace{-.2ex}:}}
\makeatletter
\newcommand{\raisemath}[1]{\mathpalette{\raisem@th{#1}}}
\newcommand{\raisem@th}[3]{\raisebox{#1}{$#2#3$}}
\makeatother

@@

\TODO{
Xudong: Detailed description of the implementation\\\\
5.1 Generation of the Open Transition\\\\
5.1.1 fresh variable\\\\
The variable in each SV are considered local, so does the variable of an open transition such as its hole behavior and its result action.
So we want rename them to make them unique, while we also hope them readable. The fresh variable has a confirmed format.
As pNets has a tree-like structure, we give every node of the pNets a tree index. And give them some counters to count the current times the SV, Hole or subnet is used, and the number of possible OT generated. \\\\
| format of fresh variable |\\\\
5.1.2 predicate generation\\\\
Combining, present all the possible working status of subnets. \\
Mixing, match the elements of the combination to match the elements of the SV one by one to generate terms of a predicate.\\\\
5.1.3 assignment\\\\
Management of state variables.\\
Translating assignments into predicate terms.\\\\
5.2 Pruning the unsatisfiable results\\\\
Interaction with Z3: pNets module ---input--> Z3 module [JAVA API]\\\\
5.2.1 presentation\\\\
5.2.2 checking satisfiability\\\\
After we get the result OTs, for each result OT, declare the variables and assertions in the Java API. Conduct checking method and get the result.\\
}

\ERIC{
=> Context VCE, ref to FASE paper\\
=> Current prototype: programatic creation of pNet objects, through the pNet API in VCE. On the middle term, this should be compiled from some language or graphical formalism.\\
=> Open transitions are computed as a direct implementation of the algorithm above. Steps 2a-2b are merged: at each pNet node, after application of rule Tr2, the resulting OT is built from the premisses, without explicitely constructing the deduction tree. \\
=> Variable names are generated for all ``fresh'' and ``clone''
operations, using structured variable names ensuring uniqueness of
fresh names, but also reasonable readability of these names for
debugging purposes.\\
=> Assignements\\
=> Satisfiability check is done only at toplevel of the deduction tree construction. An alternative would be to submit the satisfiability check to the SMT solver at each level of the tree construction, potentialy reducing the overall number of combinations. But submission to the SMT engine is costly, and more complexity analysis is required before deciding if this would be worthwhile.\\
=> Simplification is not yet implemented. It is not strictly required for the Open Automaton construction, but it will be critical later for predicate comparison in the bisimulation algorithm.}

>>>>

%\usepackage{amsfonts}
%\usepackage{fancyhdr}
%\usepackage{cite}
%\usepackage{ifthen}
%\usepackage{amssymb}
%\usepackage{fancyhdr}
%\usepackage{pifont}
\usepackage{stmaryrd}
\usepackage{mathtools,mathpartir}
\usepackage{proof}
%\usepackage{setspace}
%\usepackage{indentfirst}
\usepackage{amsmath,amssymb,amscd,mathrsfs}
\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}
\usepackage{epsfig,color,subfigure,enumitem}
\newcommand{\TODO}[1]{\textcolor{red}{\textbf{[TODO:#1]}}}
\newcommand{\NOTE}[1]{\textcolor{blue}{\textbf{[NOTE:#1]}}}
\newcommand{\ERIC}[1]{\textcolor{blue}{#1}}
\definecolor{airforceblue}{rgb}{0.36, 0.54, 0.66}
\newcommand{\QIN}[1]{\textcolor{airforceblue}{#1}}
\newcommand{\coloncolon}{{:\hspace{-.2ex}:}}
\makeatletter
\newcommand{\raisemath}[1]{\mathpalette{\raisem@th{#1}}}
\newcommand{\raisem@th}[3]{\raisebox{#1}{$#2#3$}}
\makeatother

@@

\TODO{Xudong: Detailed description of the implementation}
\QIN{
\\
5.1 Generation of the Open Transition\\\\
5.1.1 fresh variable\\\\
The variable in each SV are considered local, so does the variable of an open transition such as its hole behavior and its result action.
So we want rename them to make them unique, while we also hope them readable. The fresh variable has a confirmed format.
As pNets has a tree-like structure, we give every node of the pNets a tree index. And give them some counters to count the current times the SV, Hole or subnet is used, and the number of possible OT generated. \\\\
| format of fresh variable |\\\\
5.1.2 predicate generation\\\\
Combining, present all the possible working status of subnets. \\
Mixing, match the elements of the combination to match the elements of the SV one by one to generate terms of a predicate.\\\\
5.1.3 assignment\\\\
Management of state variables.\\
Translating assignments into predicate terms.\\\\
5.2 Pruning the unsatisfiable results\\\\
Interaction with Z3: pNets module ---input--> Z3 module [JAVA API]\\\\
5.2.1 presentation\\\\
5.2.2 checking satisfiability\\\\
After we get the result OTs, for each result OT, declare the variables and assertions in the Java API. Conduct checking method and get the result.\\
}
\ERIC{
=> Context VCE, ref to FASE paper\\
=> Current prototype: programatic creation of pNet objects, through the pNet API in VCE. On the middle term, this should be compiled from some language or graphical formalism.\\
=> Open transitions are computed as a direct implementation of the algorithm above. Steps 2a-2b are merged: at each pNet node, after application of rule Tr2, the resulting OT is built from the premisses, without explicitely constructing the deduction tree. \\
=> Variable names are generated for all ``fresh'' and ``clone''
operations, using structured variable names ensuring uniqueness of
fresh names, but also reasonable readability of these names for
debugging purposes.\\
=> Assignements\\
=> Satisfiability check is done only at toplevel of the deduction tree construction. An alternative would be to submit the satisfiability check to the SMT solver at each level of the tree construction, potentialy reducing the overall number of combinations. But submission to the SMT engine is costly, and more complexity analysis is required before deciding if this would be worthwhile.\\
=> Simplification is not yet implemented. It is not strictly required for the Open Automaton construction, but it will be critical later for predicate comparison in the bisimulation algorithm.}
